---
title: "UCLA_Regression-V2"
author: "Kyle Baacke"
date: "8/20/2022"
output: html_document
---


# Imports
```{r, echo=FALSE, include=FALSE, redults='hide'}
# install.packages("corrplot")
# install.packages("lmSupport")
library(corrplot)
library(stats)
library(car)
library(QuantPsyc)
# library(lmSupport)
library(dplyr)
```

# Read in Data

```{r}
# phen_acc_schz <- read.csv('C:/Users/sarah/Local_Documents/Data/UCLA_Data/phen_acc_schz.csv')
# phen_acc_bipolar <- read.csv('C:/Users/sarah/Local_Documents/Data/UCLA_Data/phen_acc_bipolar.csv')
# phen_acc_schz <- read.csv('C:/Users/sarah/Local_Documents/Data/UCLA_Data/phen_acc_schz-v2.csv')
# phen_acc_bipolar <- read.csv('C:/Users/sarah/Local_Documents/Data/UCLA_Data/phen_acc_bipolar-v2.csv')
phen_acc_schz <- read.csv('C:/Users/kyle/UWM/SRP Paper 01-Group - Documents/UCLA_Decoding_v2/phen_acc_schz-v2.csv')
phen_acc_bipolar <- read.csv('C:/Users/kyle/UWM/SRP Paper 01-Group - Documents/UCLA_Decoding_v2/phen_acc_bipolar-v2.csv')
```

# Standardize values of interest

```{r}
standardized_columns = c()
scale_prefixes = c('saps','sans','bipolarii')
for(prefix in scale_prefixes){
  prefix_cols_schz = colnames(phen_acc_schz[,grepl(prefix, colnames(phen_acc_schz))])
  for(col in prefix_cols_schz){
    if ((min(phen_acc_schz[,col], na.rm = TRUE)==0) & (max(phen_acc_schz[,col], na.rm = TRUE)==1)){
      # print(paste('SCHZ column with only two levels: ',col, sep = ''))
      standardized_columns = c(standardized_columns, c(col))
    } else {
      std_colname = paste(col, '_z', sep='')
      phen_acc_schz[,std_colname] = scale(phen_acc_schz[,col])
      standardized_columns = c(standardized_columns, c(std_colname))
      phen_acc_schz[,col] = NULL
    }
    
  }
  prefix_cols_bipolar = colnames(phen_acc_bipolar[,grepl(prefix, colnames(phen_acc_bipolar))])
  for(col in prefix_cols_bipolar){
    if ((min(phen_acc_bipolar[,col], na.rm = TRUE)==0) & (max(phen_acc_bipolar[,col], na.rm = TRUE)==1)){
      # print(paste('Bipolar column with only two levels: ',col, sep = ''))
      standardized_columns = c(standardized_columns, c(col))
    } else {
      std_colname = paste(col, '_z', sep='')
      phen_acc_bipolar[,std_colname] = scale(phen_acc_bipolar[,col])
      standardized_columns = c(standardized_columns, c(std_colname))
      phen_acc_bipolar[,col] = NULL
    }
  }
}

```

# Predictor management

## Remove columns with NA Values

```{r}
phen_acc_schz <- phen_acc_schz[,colSums(is.na(phen_acc_schz))<nrow(phen_acc_schz)]
phen_acc_bipolar <- phen_acc_bipolar[,colSums(is.na(phen_acc_bipolar))<nrow(phen_acc_bipolar)]

standardized_columns = unique(standardized_columns)
phen_acc_bipolar$Male = ifelse(phen_acc_bipolar$gender_x=='M', 1, 0)
phen_acc_schz$Male = ifelse(phen_acc_schz$gender_x=='M', 1, 0)
```

## Generate lists of standardized predictors in each scale

```{r}
model_string_start = "rate_misclass ~ "
saps_predictors = c(standardized_columns[grepl('saps', standardized_columns)])
sans_predictors = c(standardized_columns[grepl('sans', standardized_columns)])
bipolar_predictors = c(standardized_columns[grepl('bipolarii', standardized_columns)])
```

## Schiz

### Factor level analysis

```{r}
factor_model_schz = lm(
  rate_misclass ~ 
    factor_avolition + # "average items SANS12, SANS13, SANS14, SANS15"
    factor_bluntaffect + # "average items SANS1, SANS2, SANS3, SANS4, SANS5, SANS6"
    factor_alogia + # "average items SANS8, SANS9, SANS10"
    factor_anhedonia + # "average items SANS17, SANS18, SANS19, SANS20"
    factor_attention + # "average items SANS22, SANS23"
    factor_bizarrebehav + # "average SAPS items 21-24"
    factor_posformalthought + # "average SAPS items 26-33"
    factor_delusions + # "average SAPS items 8-19"
    factor_hallucinations + # "average SAPS items 1, 2, 3, 4, 5, 6",
    factor_inappaffect + # "item SAPS35"
    bipollarii_mood + # "Factor 1-Mood Liability: Questions 1-9 (item 7 reverse scored)"
    bipollarii_daydreaming + # "Factor 3-Daydreaming: Questions 18-23 (item 20 reverse scored)"
    bipollarii_energy + # "Factor 2-Energy-Activity: Questions 10-17"
    bipollarii_anxiety + # "Factor 4-Social Anxiety: Questions 24-31 (item 29 reverse scored)"
    age_x +
    Male
    , 
  data = phen_acc_schz
  )

summary(factor_model_schz)

schz_factor_step = step(factor_model_schz, direction = 'backward', trace = FALSE)
schz_final_factor_model = lm(schz_factor_step$call$formula, data = phen_acc_schz)

summary(schz_final_factor_model)
sort(vif(schz_final_factor_model),decreasing =T)
sort(lm.beta(schz_final_factor_model),decreasing =T)
# modelEffectSizes(schz_final_factor_model, Digits = 2)
```


Note: We cannot start with all predictors from all scales because we would have more predictors than observations

### SAPS

#### Generate model string

```{r}
schz_saps_predictor_string = paste(c(saps_predictors[saps_predictors %in% colnames(phen_acc_schz)], c('Male','age_x')), collapse = ' + ')
schz_saps_model_string = paste(model_string_start, schz_saps_predictor_string, sep = '')
```

#### Backward stepwise regression

```{r}
full_model_schiz_saps = lm(schz_saps_model_string, data = phen_acc_schz)
schiz_saps_step = step(full_model_schiz_saps, direction = 'backward', trace = FALSE)
schiz_saps_step
```

#### Results from final model

```{r}
final_model_schz_saps = lm(schiz_saps_step$call$formula, data = phen_acc_schz)

summary(final_model_schz_saps)
sort(vif(final_model_schz_saps),decreasing =T)
sort(lm.beta(final_model_schz_saps),decreasing =T)
# modelEffectSizes(final_model_schz_saps, Digits = 2)
```
#### Handling multicolinearity

```{r}
final_model_schz_saps_2 = lm(
  formula = rate_misclass ~ 
    saps1_z + 
    # saps30_z + 
    saps11_z + 
    saps18_z + saps29_z + saps23_z + saps31_z + saps33_z + saps5_z + 
    # saps19_z + 
    saps14_z + saps8_z + saps2_z + saps15_z + saps25_z + 
    # saps3_z + 
    saps34_z
  , data = phen_acc_schz
)

summary(final_model_schz_saps_2)
sort(vif(final_model_schz_saps_2),decreasing =T)
sort(lm.beta(final_model_schz_saps_2),decreasing =T)
# modelEffectSizes(final_model_schz_saps, Digits = 2)
```

### SANS

#### Generate model string

```{r}
schz_sans_predictor_string = paste(c(sans_predictors[sans_predictors %in% colnames(phen_acc_schz)], c('Male','age_x')), collapse = ' + ')
schz_sans_model_string = paste(model_string_start, schz_sans_predictor_string, sep = '')
```

#### Backward stepwise regression

```{r}
full_model_schiz_sans = lm(schz_sans_model_string, data = phen_acc_schz)
schiz_sans_step = step(full_model_schiz_sans, direction = 'backward', trace = FALSE)
schiz_sans_step
```

#### Results from final model

```{r}
final_model_schz_sans = lm(schiz_sans_step$call$formula, data = phen_acc_schz)

summary(final_model_schz_sans)
sort(vif(final_model_schz_sans),decreasing =T)
sort(lm.beta(final_model_schz_sans),decreasing =T)
# modelEffectSizes(final_model_schz_sans, Digits = 2)
```

#### Handling multicolinearity

### BIPOLARII

#### Generate model string

```{r}
schz_bipolar_predictor_string = paste(c(bipolar_predictors[bipolar_predictors %in% colnames(phen_acc_schz)], c('Male','age_x')), collapse = ' + ')
schz_bipolar_model_string = paste(model_string_start, schz_bipolar_predictor_string, sep = '')
```

#### Backward stepwise regression

```{r}
full_model_schiz_bipolar = lm(schz_bipolar_model_string, data = phen_acc_schz)
schiz_bipolar_step = step(full_model_schiz_bipolar, direction = 'backward', trace = FALSE)
schiz_bipolar_step
```

#### Results from final model

```{r}
final_model_schz_bipolar = lm(schiz_bipolar_step$call$formula, data = phen_acc_schz)

summary(final_model_schz_bipolar)
sort(vif(final_model_schz_bipolar),decreasing =T)
sort(lm.beta(final_model_schz_bipolar),decreasing =T)
# modelEffectSizes(final_model_schz_bipolar, Digits = 2)

```

#### Handling multicolinearity

### SAPS + SAPS final models

#### Backward stepwise regression

```{r}
full_model_schiz_sans_saps = lm(
  formula = rate_misclass ~ saps1_z + saps30_z + saps11_z + 
    saps18_z + saps29_z + saps23_z + saps31_z + saps33_z + saps5_z + 
    saps19_z + saps14_z + saps8_z + saps2_z + saps15_z + saps25_z + 
    saps3_z + saps34_z + sans2_z + sans16_z + sans21_z + 
    sans14_z + sans13_z + sans4_z + sans23_z + sans3_z + sans11_z + 
    sans15_z + sans12_z + sans8_z + Male
  ,data = phen_acc_schz
)
schiz_sans_saps_step = step(full_model_schiz_sans_saps, direction = 'backward', trace = FALSE)
schiz_sans_saps_step
```

#### Results from final model

```{r}
final_model_schz_sans_saps = lm(schiz_sans_saps_step$call$formula, data = phen_acc_schz)

summary(final_model_schz_sans_saps)
sort(vif(final_model_schz_sans_saps),decreasing =T)
sort(lm.beta(final_model_schz_sans_saps),decreasing =T)
# modelEffectSizes(final_model_schz_sans_saps, Digits = 2)

```

### (SAPS + SANS) + BIPOLARII

#### Backward stepwise regression

```{r}
full_model_schiz_combined = lm(rate_misclass ~ saps30_z + saps11_z + saps18_z + 
    saps31_z + saps33_z + saps19_z + saps14_z + saps8_z + saps15_z + 
    saps3_z + sans2_z + sans16_z + sans21_z + sans14_z + sans23_z + 
    sans3_z + sans11_z + sans15_z + sans12_z + sans8_z + Male + 
    bipolarii11 + bipolarii12 + bipolarii10 + 
    bipolarii8 + bipolarii27 + bipolarii19 + bipolarii1 + bipolarii6 + 
    bipolarii15 + bipolarii21 + bipolarii20 + bipolarii13 + bipolarii14 + 
    bipolarii24 + bipolarii25 + bipolarii18 + bipolarii28
    , data = phen_acc_schz)
schiz_combined_step = step(full_model_schiz_combined, direction = 'backward', trace = FALSE)
schiz_combined_step
```

#### Results form final model

Interestingly, all the bipolarii items were eliminated in the stepwise regression procedure when including them in the full model with the selected saps and sans items.

```{r}
final_model_schz_combined = lm(formula = schiz_combined_step$call$formula, data = phen_acc_schz)

summary(final_model_schz_combined)
sort(vif(final_model_schz_combined),decreasing =T)
sort(lm.beta(final_model_schz_combined),decreasing =T)
# modelEffectSizes(final_model_schz_combined, Digits = 2)

```

#### Handling multicolinearity
```{r}
final_model_schz_combined_2 = lm(
  formula = rate_misclass ~ 
    # saps30_z + 
    saps11_z +
    # saps18_z + 
    saps31_z + saps33_z + saps19_z + saps14_z + saps8_z + saps15_z + 
    sans2_z + sans16_z + sans21_z + 
    # sans3_z + 
    # sans11_z + 
    sans15_z + 
    sans12_z + sans8_z + Male + bipolarii11 + bipolarii10 + bipolarii27 + 
    bipolarii19 + bipolarii1 + bipolarii15 + bipolarii21 + bipolarii20 + 
    bipolarii13 + bipolarii14 + bipolarii24 + 
    # bipolarii18 + 
    bipolarii28, data = phen_acc_schz)

summary(final_model_schz_combined_2)
sort(vif(final_model_schz_combined_2),decreasing =T)
sort(lm.beta(final_model_schz_combined_2),decreasing =T)
# modelEffectSizes(final_model_schz_combined, Digits = 2)

```

## Bipolar

### Factor level analysis

```{r}

factor_model_bipolar = lm(
  rate_misclass ~ 
    factor_avolition + # "average items SANS12, SANS13, SANS14, SANS15"
    factor_bluntaffect + # "average items SANS1, SANS2, SANS3, SANS4, SANS5, SANS6"
    factor_alogia + # "average items SANS8, SANS9, SANS10"
    factor_anhedonia + # "average items SANS17, SANS18, SANS19, SANS20"
    factor_attention + # "average items SANS22, SANS23"
    factor_bizarrebehav + # "average SAPS items 21-24"
    factor_posformalthought + # "average SAPS items 26-33"
    factor_delusions + # "average SAPS items 8-19"
    factor_hallucinations + # "average SAPS items 1, 2, 3, 4, 5, 6",
    factor_inappaffect + # "item SAPS35"
    bipollarii_mood + # "Factor 1-Mood Liability: Questions 1-9 (item 7 reverse scored)"
    bipollarii_daydreaming + # "Factor 3-Daydreaming: Questions 18-23 (item 20 reverse scored)"
    bipollarii_energy + # "Factor 2-Energy-Activity: Questions 10-17"
    bipollarii_anxiety + age_x + Male# "Factor 4-Social Anxiety: Questions 24-31 (item 29 reverse scored)"
    , 
  data = phen_acc_bipolar,
  na.action = na.exclude
  )

summary(factor_model_bipolar)

bipolar_factor_df = phen_acc_bipolar[,names(factor_model_bipolar$model)]
bipolar_factor_df = bipolar_factor_df[complete.cases(bipolar_factor_df),]
factor_model_bipolar = lm(
  rate_misclass ~ 
    factor_avolition + # "average items SANS12, SANS13, SANS14, SANS15"
    factor_bluntaffect + # "average items SANS1, SANS2, SANS3, SANS4, SANS5, SANS6"
    factor_alogia + # "average items SANS8, SANS9, SANS10"
    factor_anhedonia + # "average items SANS17, SANS18, SANS19, SANS20"
    factor_attention + # "average items SANS22, SANS23"
    factor_bizarrebehav + # "average SAPS items 21-24"
    factor_posformalthought + # "average SAPS items 26-33"
    factor_delusions + # "average SAPS items 8-19"
    factor_hallucinations + # "average SAPS items 1, 2, 3, 4, 5, 6",
    factor_inappaffect + # "item SAPS35"
    bipollarii_mood + # "Factor 1-Mood Liability: Questions 1-9 (item 7 reverse scored)"
    bipollarii_daydreaming + # "Factor 3-Daydreaming: Questions 18-23 (item 20 reverse scored)"
    bipollarii_energy + # "Factor 2-Energy-Activity: Questions 10-17"
    bipollarii_anxiety + age_x + Male# "Factor 4-Social Anxiety: Questions 24-31 (item 29 reverse scored)"
    , 
  data = bipolar_factor_df,
  na.action = na.exclude
  )

bipolar_factor_step = step(factor_model_bipolar, direction = 'backward', trace = FALSE)
bipolar_final_factor_model = lm(bipolar_factor_step$call$formula, data = phen_acc_bipolar)

summary(bipolar_final_factor_model)
sort(vif(bipolar_final_factor_model),decreasing =T)
sort(lm.beta(bipolar_final_factor_model),decreasing =T)
# modelEffectSizes(bipolar_final_factor_model, Digits = 2)
```

Note: We cannot start with all predictors from all scales because we would have more predictors than observations

### SAPS

#### Generate model string

```{r}
phen_acc_bipolar$saps10 = NULL # Thic solumn is all 0's
bipolar_saps_predictor_string = paste(c(saps_predictors[saps_predictors %in% colnames(phen_acc_bipolar)], c('Male','age_x')), collapse = ' + ')
bipolar_saps_model_string = paste(model_string_start, bipolar_saps_predictor_string, sep = '')
```

#### Backward stepwise regression

```{r}
phen_acc_bipolar_saps = phen_acc_bipolar[
  ,c(
    saps_predictors[saps_predictors %in% colnames(phen_acc_bipolar)], c('Male','age_x','rate_misclass')
    )
  ]
phen_acc_bipolar_saps = phen_acc_bipolar_saps[complete.cases(phen_acc_bipolar_saps),]
full_model_bipolar_saps = lm(bipolar_saps_model_string, data = phen_acc_bipolar_saps, na.action=na.exclude)
bipolar_saps_step = step(full_model_bipolar_saps, direction = 'backward', trace = FALSE)
bipolar_saps_step
```

#### Results from final model

```{r}
final_model_bipolar_saps = lm(bipolar_saps_step$call$formula, data = phen_acc_bipolar_saps)

summary(final_model_bipolar_saps)
sort(vif(final_model_bipolar_saps),decreasing =T)
sort(lm.beta(final_model_bipolar_saps),decreasing =T)
# modelEffectSizes(final_model_bipolar_saps, Digits = 2)

```


### SANS

#### Generate model string

```{r}
bipolar_sans_predictor_string = paste(c(sans_predictors[sans_predictors %in% colnames(phen_acc_bipolar)], c('Male','age_x')), collapse = ' + ')
bipolar_sans_model_string = paste(model_string_start, bipolar_sans_predictor_string, sep = '')
```

#### Backward stepwise regression

```{r}
phen_acc_bipolar_sans = phen_acc_bipolar[
  ,c(
    sans_predictors[sans_predictors %in% colnames(phen_acc_bipolar)], c('Male','age_x','rate_misclass')
    )
  ]
phen_acc_bipolar_sans = phen_acc_bipolar_sans[complete.cases(phen_acc_bipolar_sans),]
full_model_bipolar_sans = lm(bipolar_sans_model_string, data = phen_acc_bipolar_sans)
bipolar_sans_step = step(full_model_bipolar_sans, direction = 'backward', trace = FALSE)
bipolar_sans_step
```

#### Results from final model

```{r}
final_model_bipolar_sans = lm(bipolar_sans_step$call$formula, data = phen_acc_bipolar_sans)

summary(final_model_bipolar_sans)
sort(vif(final_model_bipolar_sans),decreasing =T)
sort(lm.beta(final_model_bipolar_sans),decreasing =T)
# modelEffectSizes(final_model_bipolar_sans, Digits = 2)

```

### BIPOLARII

#### Generate model string

```{r}
bipolar_bipolar_predictor_string = paste(c(bipolar_predictors[bipolar_predictors %in% colnames(phen_acc_bipolar)], c('Male','age_x')), collapse = ' + ')
bipolar_bipolar_model_string = paste(model_string_start, bipolar_bipolar_predictor_string, sep = '')
```

#### Backward stepwise regression

```{r}
full_model_bipolar_bipolar = lm(bipolar_bipolar_model_string, data = phen_acc_bipolar)
bipolar_bipolar_step = step(full_model_bipolar_bipolar, direction = 'backward', trace = FALSE)
bipolar_bipolar_step
```

#### Results from final model

```{r}
final_model_bipolar_bipolar = lm(formula = rate_misclass ~ bipolarii11 + bipolarii10 + bipolarii5 + 
    bipolarii22 + bipolarii27 + bipolarii16 + bipolarii20 + bipolarii18 + 
    bipolarii28 + age_x, data = phen_acc_bipolar)

summary(final_model_bipolar_bipolar)
sort(vif(final_model_bipolar_bipolar),decreasing =T)
sort(lm.beta(final_model_bipolar_bipolar),decreasing =T)
# modelEffectSizes(final_model_bipolar_bipolar, Digits = 2)

```

### SAPS + SAPS final models

#### Backward stepwise regression

saps1_z + saps30_z + saps6_z + saps23_z + 
saps20_z + saps10_z + saps26_z + saps9_z + saps22_z + saps7_z + 
saps25_z + saps13 + Male + age_x +
sans2_z + sans22_z + sans1_z + sans9_z + 
sans13_z + sans4_z + sans15_z + sans8_z


```{r}

bipolar_sans_saps_df = phen_acc_bipolar[,c(
  'saps1_z','saps30_z',
  'saps6_z','saps23_z','saps20_z','saps10_z','saps26_z','saps9_z','saps22_z','saps7_z','saps25_z','saps13','Male',
  'sans2_z','sans22_z','sans1_z',
  'sans9_z','sans13_z','sans4_z','sans15_z','sans8_z',
  'age_x',
  'rate_misclass'
  )]
bipolar_sans_saps_df = bipolar_sans_saps_df[complete.cases(bipolar_sans_saps_df),]
# View(bipolar_sans_saps_df)
full_model_bipolar_sans_saps = lm(
  formula = rate_misclass ~ saps1_z + saps30_z + saps6_z + saps23_z + 
    saps20_z + saps10_z + saps26_z + saps9_z + saps22_z + saps7_z + 
    saps25_z + saps13 + Male + age_x +
    sans2_z + sans22_z + sans1_z + sans9_z + 
    sans13_z + sans4_z + sans15_z + sans8_z, 
  data = na.omit(bipolar_sans_saps_df)
)
bipolar_sans_saps_step = step(full_model_bipolar_sans_saps, direction = 'backward', trace = FALSE)
bipolar_sans_saps_step
```

#### Results from final model

```{r}
final_model_bipolar_sans_saps = lm(
  bipolar_sans_saps_step$call$formula, data = bipolar_sans_saps_df)

summary(final_model_bipolar_sans_saps)
sort(vif(final_model_bipolar_sans_saps),decreasing =T)
sort(lm.beta(final_model_bipolar_sans_saps),decreasing =T)
# modelEffectSizes(final_model_bipolar_sans_saps, Digits = 2)

```

### (SAPS + SANS) + BIPOLARII

#### Backward stepwise regression

```{r}
full_model_bipolar_combined = lm(
  formula = rate_misclass ~ 
    saps1_z + saps30_z + saps6_z + saps23_z + 
    saps20_z + saps10_z + saps26_z + saps9_z + saps22_z + saps7_z + 
    saps25_z + saps13 + Male + age_x + sans22_z + sans4_z + sans15_z + 
    bipolarii11 + bipolarii10 + bipolarii5 + 
    bipolarii22 + bipolarii27 + bipolarii16 + bipolarii20 + bipolarii18 + 
    bipolarii28, data = phen_acc_bipolar)
bipolar_combined_step = step(full_model_bipolar_combined, direction = 'backward', trace = FALSE)
bipolar_combined_step
```

#### Results from final model

The VIFs spike dramatically when combining the saps +sans model with the bipolarii items, indicating that there may be substantial crossover in information across the variables selected by the saps+sans process and the bipolarii items selected.
The rerun is propagated from where I removed saps30_z from the saps + sans model. The resulting model has much lower VIFs, although some still higher than recommended.

```{r}
final_model_bipolar_combined = lm(bipolar_combined_step$call$formula, data = phen_acc_bipolar)

summary(final_model_bipolar_combined)
sort(vif(final_model_bipolar_combined),decreasing =T)
sort(lm.beta(final_model_bipolar_combined) ,decreasing =T)
# modelEffectSizes(final_model_bipolar_combined, Digits = 2)

```


#### Handling multiconlearity

```{r}
final_model_bipolar_combined_2 = lm(
  formula = rate_misclass ~ 
    saps1_z + saps30_z + saps23_z + 
    saps20_z + saps10_z + saps26_z + saps9_z + saps22_z + 
    # saps25_z + 
    saps13 + Male + age_x + sans22_z + sans15_z + bipolarii16 + 
    bipolarii28, 
  data = phen_acc_bipolar
)

summary(final_model_bipolar_combined_2)
sort(vif(final_model_bipolar_combined_2),decreasing =T)
sort(lm.beta(final_model_bipolar_combined_2) ,decreasing =T)

```


# Output consolidation

## Function definitions

```{r}
lm_summary_dataframe = function(subject_subset_label, variable_subset_label, lm_object){
  # subject_subset_label, variable_subset_label, terms, Adjusted_R_Squared, F, df_1, df_2, p_value, residual_SE, n_terms
  summary_obj = summary(lm_object)
  res_data_frame = data.frame(
    subject_subset = c(subject_subset_label),
    variable_subset = c(variable_subset_label),
    terms = c(toString(lm_object$terms)),
    adjusted_r_squared = c(summary_obj$adj.r.squared),
    f = c(summary_obj$fstatistic['value']), 
    df_1 = c(summary_obj$fstatistic['numdf']), 
    df_2 = c(summary_obj$fstatistic['dendf']), 
    p_value = c(pf(
      summary_obj$fstatistic['value'],
      summary_obj$fstatistic['numdf'],
      summary_obj$fstatistic['dendf'],
      lower.tail=F
      )),
    # residual_SE = c(), # TODO
    n_terms = c(length(names(lm_object$model))-1) 
  )
  return(res_data_frame)
}

lm_detail_dataframe = function(subject_subset_label, variable_subset_label, lm_object){
  # subject_subset, variable_subset, variable_name, Estimate, Std_Error, t_value, p_value, VIF, beta, partial_eta_squared
  coef_df = as.data.frame(summary(lm_object)$coefficients)
  coef_df = coef_df[c(2:length(rownames(coef_df))),]
  coef_df$variable_name = rownames(coef_df)
  coef_df$VIF = vif(lm_object)
  coef_df$beta = lm.beta(lm_object)
  # mes_object = modelEffectSizes(lm_object, Print=FALSE)
  # coef_df$partial_eta_squared = mes_object$Effects[c(2:length(rownames(mes_object$Effects))),c('pEta-sqr')]
  coef_df$subject_subset = subject_subset_label
  coef_df$variable_subset = variable_subset_label
  return(coef_df)
}

```

## Consolidate Outputs

```{r}

# Schz

## Factor
schz_factor_out = lm_summary_dataframe("schz","factor",schz_final_factor_model)
schz_factor_out_detail = lm_detail_dataframe("schz","factor",schz_final_factor_model)
## SAPS
schz_saps_out = lm_summary_dataframe("schz","saps",final_model_schz_saps)
schz_saps_out_detail = lm_detail_dataframe("schz","saps",final_model_schz_saps)
## SANS
schz_sans_out = lm_summary_dataframe("schz","sans",final_model_schz_sans)
schz_sans_out_detail = lm_detail_dataframe("schz","sans",final_model_schz_sans)
## bipolarii
schz_bipolarii_out = lm_summary_dataframe("schz","bipolarii",final_model_schz_bipolar)
schz_bipolarii_out_detail = lm_detail_dataframe("schz","bipolarii",final_model_schz_bipolar)
## SANS + SAPS
schz_sans_saps_out = lm_summary_dataframe("schz","sans+saps",final_model_schz_sans_saps)
schz_sans_saps_out_detail = lm_detail_dataframe("schz","sans+saps",final_model_schz_sans_saps)
## (SANS + SAPS) + bipolarii
schz_combined_out = lm_summary_dataframe("schz","(sans+saps)+bipolarii",final_model_schz_combined)
schz_combined_out_detail = lm_detail_dataframe("schz","(sans+saps)+bipolarii",final_model_schz_combined)

schz_combined_out_2 = lm_summary_dataframe("schz","(sans+saps)+bipolarii",final_model_schz_combined_2)
schz_combined_out_detail_2 = lm_detail_dataframe("schz","(sans+saps)+bipolarii",final_model_schz_combined_2)

# Bipolar
## Factor
bipolar_factor_out = lm_summary_dataframe("bipolar","factor",bipolar_final_factor_model)
bipolar_factor_out_detail = lm_detail_dataframe("bipolar","factor",bipolar_final_factor_model)
## SAPS
bipolar_saps_out = lm_summary_dataframe("bipolar","saps",final_model_bipolar_saps)
bipolar_saps_out_detail = lm_detail_dataframe("bipolar","saps",final_model_bipolar_saps)
## SANS
bipolar_sans_out = lm_summary_dataframe("bipolar","sans",final_model_bipolar_sans)
bipolar_sans_out_detail = lm_detail_dataframe("bipolar","sans",final_model_bipolar_sans)
## bipolarii
bipolar_bipolarii_out = lm_summary_dataframe("bipolar","bipolarii",final_model_bipolar_bipolar)
bipolar_bipolarii_out_detail = lm_detail_dataframe("bipolar","bipolarii",final_model_bipolar_bipolar)
## SANS + SAPS
bipolar_sans_saps_out = lm_summary_dataframe("bipolar","sans+saps",final_model_bipolar_sans_saps)
bipolar_sans_saps_out_detail = lm_detail_dataframe("bipolar","sans+saps",final_model_bipolar_sans_saps)
## (SANS + SAPS) + bipolarii
bipolar_combined_out = lm_summary_dataframe("bipolar","(sans+saps)+bipolarii",final_model_bipolar_combined)
bipolar_combined_out_detail = lm_detail_dataframe("bipolar","(sans+saps)+bipolarii",final_model_bipolar_combined)

bipolar_combined_out_2 = lm_summary_dataframe("bipolar","(sans+saps)+bipolarii",final_model_bipolar_combined_2)
bipolar_combined_out_detail_2 = lm_detail_dataframe("bipolar","(sans+saps)+bipolarii",final_model_bipolar_combined_2)

model_level_output = bind_rows(
  list(
    schz_factor_out,
    schz_saps_out,
    schz_sans_out,
    schz_bipolarii_out,
    schz_sans_saps_out,
    schz_combined_out,
    schz_combined_out_2,
    bipolar_factor_out,
    bipolar_saps_out,
    bipolar_sans_out,
    bipolar_bipolarii_out,
    bipolar_sans_saps_out,
    bipolar_combined_out,
    bipolar_combined_out_2
  )
)

item_level_output = bind_rows(
  list(
    schz_factor_out_detail,
    schz_saps_out_detail,
    schz_sans_out_detail,
    schz_bipolarii_out_detail,
    schz_sans_saps_out_detail,
    schz_combined_out_detail,
    schz_combined_out_detail_2,
    bipolar_factor_out_detail,
    bipolar_saps_out_detail,
    bipolar_sans_out_detail,
    bipolar_bipolarii_out_detail,
    bipolar_sans_saps_out_detail,
    bipolar_combined_out_detail,
    bipolar_combined_out_detail_2
  )
)

write.csv(model_level_output, "UCLA_model_summary_statistics-v2.csv", row.names = FALSE)
write.csv(item_level_output, "UCLA_model_item_statistics-v2.csv", row.names = FALSE)

```

